---
title: "Shiny course"
date: "October 2016"
output:
    html_document:
        theme: cerulean
        css: style.css
---

<div style="float: right; width: 33%; margin: 1em; padding: 1em; border: solid 1px #000; background: #fff8ee;">
<h2 style="margin-top: 0">Links</h2>

### Shiny

[Shiny](http://shiny.rstudio.com/)

 * [gallery](http://shiny.rstudio.com/gallery/)
 * [reference](http://shiny.rstudio.com/reference/shiny/latest/)

[Shiny Server](https://www.rstudio.com/products/shiny/download-server/)

[DT](https://rstudio.github.io/DT/) (DataTables in R)

### Bioconductor

[Bioconductor cheat sheet](https://github.com/mikelove/bioc-refcard)

[Gviz](https://bioconductor.org/packages/release/bioc/html/Gviz.html) (and see also [ggbio](https://bioconductor.org/packages/release/bioc/html/ggbio.html))
</div>
<div style="width: 66%">
This is a tutorial prepared by the [Monash Bioinformatics Platform](http://bioinformatics.erc.monash.edu/) on the Shiny library developed by RStudio, to be presented as part of a [hands on workshop at ABACBS 2016](http://www.abacbs.org/biocasia2016workshop/). Shiny provides an easy way to present R data analysis interactively and over the web.

## Setup

Before the tutorial please install RStudio, and then install packages from CRAN and Bioconductor with the following R code:

```{r eval=FALSE}
install.packages("shiny")
install.packages("DT")

source("https://bioconductor.org/biocLite.R")
biocLite(c(
    "BSgenome.Scerevisiae.UCSC.sacCer3",
    "TxDb.Scerevisiae.UCSC.sacCer3.sgdGene",
    "GenomicRanges",
    "rtracklayer",
    "Gviz"))
```

Make sure you are running R 3.3 and Bioconductor 3.3, or higher.

```{r eval=FALSE}
# To upgrade an old Bioconductor installation
source("https://bioconductor.org/biocLite.R")
biocLite("BiocUpgrade")
```
</div>

## Files

* [tutorial.R](tutorial.R) 
* [forward.bw](forward.bw) 
* [reverse.bw](reverse.bw) 

Download these files. `tutorial.R` contains all the code in the "tutorial" link below. During the tutorial, we will be stepping through `tutorial.R` in RStudio. I'm still making changes to `tutorial.R`, so please download it on the day!

## Content

* [Tutorial](http://biotraining.erc.monash.edu:3838/chaos/tutorial) ([static](tutorial.html)) ([.Rmd](tutorial.Rmd))
* [Slides](http://biotraining.erc.monash.edu:3838/chaos/slides) ([static](slides.html)) ([.Rmd](slides.Rmd))

* [Solutions to challenges](https://github.com/MonashBioinformaticsPlatform/2016-11-03-r-shiny/tree/gh-pages/solutions)

## Source code

* [GitHub repository](https://github.com/MonashBioinformaticsPlatform/2016-11-03-r-shiny)
